Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-01-13 paper.qmd
Updated Figure 9

```{r}
#| label: import-scripts
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
source("scripts/five_gau_clusters/5_gen_model_with_tsne.R")
```

@@

free(distance_points) /
  wrap_plots(trimesh_two_curvy, trimesh_two_curvy_removed2, trimesh_two_curvy_removed1, two_curvy_proj_umap_model_delaunay, two_curvy_proj_umap_model_benchmark2, two_curvy_proj_umap_first_model1_temp, ncol = 3) +
  plot_annotation(tag_levels = list(c("(a)", "(b)")))

# free(distance_points) + plot_annotation(tag_levels = 'A') +
#  (trimesh_two_curvy2 + trimesh_two_curvy_removed2 + trimesh_two_curvy_removed1 + two_curvy_proj_umap_model_delaunay + two_curvy_proj_umap_model_benchmark2 + two_curvy_proj_umap_model) +
#   plot_layout(widths = c(0.5, 1, 1, 1)) +
#   plot_annotation(tag_levels = list(c("(a)", "(b)"))) 
```

>>>>

```{r}
#| label: import-scripts
source("scripts/one_c_shaped_dens_structure/04_gen_error_plots.R")
source("scripts/five_gau_clusters/5_gen_model_with_tsne.R")
source("scripts/two_non_linear_diff_shaped_close_clusters/10_gen_rm_lg_plots.R")
```

@@

gen_tuning_lg_plots()
```
